```{r message=FALSE}
library(dplyr)
googleTrends = read.csv("/Users/markneedham/Downloads/report.csv", row.names=NULL)

```{r}
googleTrends %>% head()
googleTrends %>% sample_n(10)
googleTrends %>% tail()
```

```{r}
names(googleTrends) = c("week", "score")
```

```{r}
googleTrends %>% 
  mutate(ind = row_number()) %>% 
  group_by(ind) %>%
  mutate(dates = strsplit(week, " - "),
         start = dates[[1]][1] %>% strptime("%Y-%m-%d") %>% as.character(),
         end =   dates[[1]][2] %>% strptime("%Y-%m-%d") %>% as.character()) %>%
  head()
```

```{r}
googleTrends %>% 
  mutate(ind = row_number()) %>% 
  group_by(ind) %>%
  mutate(dates = strsplit(week, " - "),
         start = dates[[1]][1] %>% strptime("%Y-%m-%d") %>% as.character(),
         end =   dates[[1]][2] %>% strptime("%Y-%m-%d") %>% as.character()) %>%
  filter(!is.na(start) | !is.na(end)) %>% 
  head()

```

```{r}
cleanGoogleTrends = googleTrends %>% 
  mutate(ind = row_number()) %>% 
  group_by(ind) %>%
  mutate(dates = strsplit(week, " - "),
         start = dates[[1]][1] %>% strptime("%Y-%m-%d") %>% as.character(),
         end =   dates[[1]][2] %>% strptime("%Y-%m-%d") %>% as.character()) %>%
  filter(!is.na(start) | !is.na(end)) %>%
  ungroup() %>%
  select(-c(ind, dates, week))

cleanGoogleTrends %>% head()
cleanGoogleTrends %>% sample_n(10)
cleanGoogleTrends %>% tail()
```

```{r}
library(ggplot2)
ggplot(aes(x = start, y = score), data = cleanGoogleTrends) + 
  geom_line(size = 0.5)
```

```{r}
cleanGoogleTrends = cleanGoogleTrends %>% mutate(start =  as.Date(start))
ggplot(aes(x = start, y = score), data = cleanGoogleTrends) + 
  geom_line(size = 0.5)
```

```{r}
class(cleanGoogleTrends$score)
```

```{r}
cleanGoogleTrends = cleanGoogleTrends %>% mutate(score = as.numeric(score))
ggplot(aes(x = start, y = score), data = cleanGoogleTrends) + 
  geom_line(size = 0.5)
```

```{r message=FALSE, warning=FALSE}
library(zoo)
cleanGoogleTrends = cleanGoogleTrends %>% 
  mutate(rolling = rollmean(score, 4, fill = NA, align=c("right")))

ggplot(aes(x = start, y = rolling), data = cleanGoogleTrends) + 
  geom_line(size = 0.5)
```


```{r warning=FALSE}
library(dplyr)
library(zoo)
library(ggplot2)

googleTrends = read.csv("/Users/markneedham/Downloads/report.csv", row.names=NULL)
names(googleTrends) = c("week", "score")

cleanGoogleTrends = googleTrends %>% 
  mutate(ind = row_number()) %>% 
  group_by(ind) %>%
  mutate(dates = strsplit(week, " - "),
         start = dates[[1]][1] %>% strptime("%Y-%m-%d") %>% as.character(),
         end =   dates[[1]][2] %>% strptime("%Y-%m-%d") %>% as.character()) %>%
  filter(!is.na(start) | !is.na(end)) %>%
  ungroup() %>%
  select(-c(ind, dates, week)) %>%
  mutate(start =  as.Date(start),
         score = as.numeric(score),
         rolling = rollmean(score, 4, fill = NA, align=c("right")))

ggplot(aes(x = start, y = rolling), data = cleanGoogleTrends) + 
  geom_line(size = 0.5)
```

```{r}
library(dplyr)
data = data.frame(week = c("2014-01-01 - 2014-02-07", "2014-01-08 - 2014-02-14", "foo"), stringsAsFactors=FALSE)
data %>% mutate(dates = strsplit(week, " - "), start = dates[[row_number()]])
data %>% 
  mutate(ind = row_number()) %>% 
  group_by(ind) %>%
  mutate(dates = strsplit(week, " - "))
```