The meetup social network
========================================================

```{r message=FALSE}
library(RNeo4j)
library(dplyr)
library(igraph)
```

```{r}
graph = startGraph("http://localhost:7474/db/data/")
options(width = 200)
options("scipen"=100, "digits"=4)
```

### Who's at the centre of London's NoSQL meetup scene?

We want to find out who's the most influential person in the London NoSQL meetup scene which we'll calculate based on assuming relationships between a pair of people if they've both attended the same meetup.


```{r}
nodes_query = "MATCH (p:MeetupProfile)-[:RSVPD]->({response: 'yes'})-[:TO]->(event)
               RETURN DISTINCT ID(p) AS id, p.id AS name, p.name AS fullName"

nodes = cypher(graph, nodes_query)

edges_query = "MATCH (p:MeetupProfile)-[:RSVPD]->({response: 'yes'})-[:TO]->(event),
                     (event)<-[:TO]-({response:'yes'})<-[:RSVPD]-(other)
               WHERE ID(p) < ID(other)
               RETURN ID(p) AS source, ID(other) AS target, COUNT(*) AS weight"

edges = cypher(graph, edges_query)
```

### Betweenness Centrality

We can use igraph's `betweenness` function to find out which person has the most shortest paths running through them:

```{r}
g = graph.data.frame(edges, directed = F, nodes)

bw = betweenness(g)
bwDf = data.frame(id = names(bw), score = bw)
bwDf %>% arrange(desc(score)) %>%  head()

merge(nodes, bwDf, by.x = "name", by.y = "id") %>% 
  arrange(desc(score)) %>% 
  head(10)
```

Now that  we've got those values let's write them into the graph:

```{r eval=FALSE}
query = "MATCH (p:MeetupProfile {id: {id}}) SET p.betweenness = {score}"

tx = newTransaction(graph)

for(i in 1:nrow(bwDf)) {
  if(i %% 1000 == 0) {
    commit(tx)
    print(paste("Batch", i / 1000, "committed."))
    tx = newTransaction(graph)
  }
  id = bwDf[i, "id"]
  score = bwDf[i, "score"]    
  appendCypher(tx,
               query,
               id = id,
               score = as.double(score))
}

commit(tx)
```

### Page Rank

Calculating page rank is as simple as calling the `page.rank` function:

```{r}
pr = page.rank(g)$vector
prDf = data.frame(name = names(pr), rank = pr) %>% arrange(desc(rank))

merge(nodes, prDf, by.x = "name", by.y = "name") %>%
  arrange(desc(rank)) %>%
  head(10)
```

We can now write the page rank back into the graph for use in future queries.

```{r eval=FALSE}
query = "MATCH (p:MeetupProfile {id: toInt({id})}) SET p.pageRank = toFloat({score})"

tx = newTransaction(graph)

for(i in 1:nrow(prDf)) {
  if(i %% 1000 == 0) {
    commit(tx)
    print(paste("Batch", i / 1000, "committed."))
    tx = newTransaction(graph)
  }
  name = prDf[i, "name"]
  rank = prDf[i, "rank"]    
  appendCypher(tx,
               query,
               id = name,
               score = as.double(rank))
}

commit(tx)
```