# Data setup

```{r message=FALSE}
library(lubridate)
library(dplyr)
```

```{r}
set.seed(1)
group1Counts = as.integer(cumsum(runif(10,1,10)))
group1Dates = ymd_hms("2011-01-01 17:00:00") + c(1) * days(group1Counts)

set.seed(3)
group2Counts = as.integer(cumsum(runif(10,1,10)))
group2Dates = ymd_hms("2011-01-10 17:00:00") + c(1) * days(group2Counts)

g1 = merge(c("Group1"), group1Counts) %>% mutate(date = group1Dates)
g2 = merge(c("Group2"), group2Counts) %>% mutate(date = group2Dates)

g = rbind(g1, g2)
names(g) = c("name", "count", "date")
g
```

## How many members in Group 1 on 24th February 2011 and Group 2 on 18th February 2011?

We should get 51 for Group 1 and 37 for Group 2

### Non vectorised

```{r}
events = data.frame(eventId = c(1,2), group = c("Group1", "Group2"), eventDate = c(ymd("2011-02-24"), ymd("2011-02-18")))
events
```

```{r}
getCount =  function(g, group, eventDate) {
  (g %>% filter(name == group & eventDate > date) %>% do(tail(., 1)))$count
}

events %>% 
  mutate(ind = row_number()) %>% group_by(ind) %>%
  mutate(count = getCount(g, group, eventDate)) %>% 
  ungroup() %>% select(-ind)
```

### Vectorised

```{r}
getCountV =  function(g, group, eventDate) {
  (g %>% filter(name == group & eventDate > date) %>% do(tail(., 1)))$count
}

events %>% mutate(count = getCountV(g, group, eventDate))
```

That result isn't correct...effectively it's doing this:

```{r}
g %>% 
  filter(name == c("Group1", "Group2") & c(ymd("2011-02-24"), ymd("2011-02-18")) > date)
```

but it isn't coming back with the correct rows for Group1, it's like it only applied the second date?

```{r}
g %>% 
  filter(name == c("Group1") & c(ymd("2011-02-24")) > date)

g %>% 
  filter(name == c("Group1") & c(ymd("2011-02-18")) > date)
```

but even then it seems to be skipping off half of the rows on the data frame which comes back.

### Trying out rank

```{r}
min_rank(desc(H))
getCountV2 =  function(g, group, eventDate) {
  result = g %>% filter(name == group & difftime(eventDate, date) > 0)
  print(result %>% mutate(rank = min_rank(count)))
  (result %>% do(tail(., 1)))$count
}

events %>% mutate(count = getCountV2(g, group, eventDate))
```