Where do people go to meetups?
========================================================

So we already know which days of the week and months of the year people attend meetups but where abouts in London are those meetups being held?

First things first, let's load in the required libraries:

```{r message=FALSE}
library(RNeo4j)
library(dplyr)
library(ggplot2)
library(ggmap)
library(grid)
library(geosphere)
library(cluster)
```


```{r}
graph = startGraph("http://localhost:7474/db/data/")
options(width = 200)
```

```{r}
query = "MATCH (g:Group)-[:HOSTED_EVENT]->(event)<-[:TO]-({response: 'yes'})<-[:RSVPD]-(),
               (event)-[:HELD_AT]->(venue)
         WHERE (event.time + event.utc_offset) < timestamp()
         RETURN g.name, 
                event.time + event.utc_offset AS eventTime,
                event.announced_at AS announcedAt, 
                event.name, 
                COUNT(*) AS rsvps, 
                venue.name AS venue, venue.lat AS lat, venue.lon AS lon"

events = cypher(graph, query)

byVenue = events %>% 
  count(lat, lon, venue) %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  rename(count = n)

byVenue %>% head(10)
```

Skillsmatter is first as you'd probably expect - there are a lot of meetups going on here. Let's have a look what's happening in the rest of London:

```{r fig.width=15, fig.height=10, warning = FALSE, message = FALSE}
map = get_map(location = 'London', zoom = 12)

ggmap(map) +
  geom_point(aes(x = lon, y = lat, size = count), 
             data = byVenue,
             col = "red",
             alpha = 0.8) + 
  theme(plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm"))
```

Clustering venues
-------------

```{r}
clusteramounts = 40
distance.matrix = byVenue %>% select(lon, lat) %>% distm
clustersx <- agnes(distance.matrix, diss = T) %>% as.hclust
byVenue$group <- cutree(clustersx, k=clusteramounts)
```


```{r}
byVenue %>% group_by(group) %>% summarise(events = sum(count)) %>% arrange(desc(events)) %>% head(10)
```


```{r}
byVenueClustered = byVenue %>% 
  group_by(group) %>% 
  summarise(meanLat = mean(lat),
            meanLon = mean(lon),
            total = sum(count)) %>%
  arrange(desc(total))   
byVenueClustered %>% head(10)
```

```{r fig.width=15, fig.height=10, warning = FALSE, message = FALSE}
ggmap(map) +
  geom_point(aes(x = meanLon, y = meanLat, size = total), 
             data = byVenueClustered,
             col = "red",
             alpha = 0.8)
```

### The meetup quadrangle

We can now see 4 big clusters - Skillsmatter as we identified before, one south of the River, one over in Westminster and the biggest cluster over in Shoreditch / Liverpool Street.

First let's grab those groups:

```{r}
topGroups = (byVenueClustered %>% head(4))$group
topGroups
```


```{r}
merge(byVenue, byVenueClustered, by.id = "group") %>% 
  filter(group %in% topGroups) %>% 
  select(group, venue, count, total) %>% 
  arrange(desc(total))
```