

```{r message=FALSE}
library(RNeo4j)
library(dplyr)
library(car)
library(geosphere)
library(ggplot2)

graph = startGraph("http://localhost:7574/db/data/")
timestampToDate = function(x) as.POSIXct(x / 1000, origin="1970-01-01", tz = "GMT")
```

```{r}
# london nosql events
query = "MATCH (g:Group)-[:HOSTED_EVENT]->(event)<-[:TO]-({response: 'yes'})<-[:RSVPD]-(),
               (event)-[:HELD_AT]->(venue)
         WHERE (event.time + event.utc_offset) < timestamp()
         WITH g, event, COUNT(*) AS rsvps, venue.name AS venue,venue.lat AS lat,venue.lon AS lon
         OPTIONAL MATCH (event)-[:HAPPENED_ON]->(day)<-[:HAPPENED_ON]-(other:Event) WHERE other <> event
  	     OPTIONAL MATCH (other)<-[:TO]-(:RSVP {response: 'yes'})<-[:RSVPD]-(:MeetupProfile)
         WITH g, event, rsvps, venue, lat, lon, COLLECT(DISTINCT other) AS otherEvents, COLLECT(other) AS otherEventsPeople
         RETURN g.name, event.id,
                event.time + event.utc_offset AS eventTime,
                event.name, 
                rsvps, 
                venue,
                lat,
                lon, 
                LENGTH(otherEvents) AS numberOfOtherEvents,
                LENGTH(otherEventsPeople) AS numberOfPeopleGoingToOtherEvents
         ORDER BY rsvps DESC"

events = cypher(graph, query)
events$eventTime <- timestampToDate(events$eventTime)
events$time = format(events$eventTime, "%H:%M")
events$day <- format(events$eventTime, "%A")
events$dayOfMonth <- as.numeric(format(events$eventTime, "%d"))
events$monthYear <- format(events$eventTime, "%m-%Y")
events$month <- factor(format(events$eventTime, "%B"), levels = month.name)
events$year <- format(events$eventTime, "%Y")
events %>% head()
```


## Is the RSVP data normally distributed?

```{r}
shapiro.test(events$rsvps)
ggplot(aes(x = rsvps), data = events) + geom_histogram(binwidth = 10)
ggplot(aes(x = log(rsvps)), data = events) + geom_histogram(binwidth = 1)
```

```{r}
query = "MATCH (g:Group)<-[:MEMBER_OF]-()
WITH g, COUNT(*) AS max
ORDER BY max DESC
match (:Person)-[:HAS_MEETUP_PROFILE]->()-[:HAS_MEMBERSHIP]->(membership)-[:OF_GROUP]->(g:Group)
RETURN g.name, membership.joined AS joinTimestamp, max"
meetupMembers = cypher(graph, query)
meetupMembers$joinDate <- timestampToDate(meetupMembers$joinTimestamp)
meetupMembers$dayMonthYear <- as.Date(meetupMembers$joinDate)

cumulativeMeetupMembers = meetupMembers %>% 
  group_by(g.name, dayMonthYear) %>% 
  summarise(n = n()) %>%
  mutate(n = cumsum(n))

write.csv(cumulativeMeetupMembers, "/tmp/cumulativeMeetupMembers.csv", row.names = FALSE)

memberCount = function(meetupMembers) {
  function(groupName, date) {
    (meetupMembers %>% 
       filter(g.name == groupName & dayMonthYear < date) %>% do(tail(., 1)))$n    
  }  
} 

findMemberCount = memberCount(cumulativeMeetupMembers)

membersWithGroupCounts= events %>%
  mutate(
    groupMembers = by(events, 1:nrow(events), function(row) { 
        findMemberCount(row$g.name, as.character(row$eventTime))
      }) %>% 
      cbind() %>% 
      as.vector()    
    )

membersWithGroupCounts %>% 
  filter(g.name == "Neo4j - London User Group") %>% 
  arrange(eventTime) %>%
  select(rsvps, groupMembers, month, year) %>%
  sample_n(10)

write.csv(membersWithGroupCounts, "/tmp/membersWithGroupCounts.csv")

ggplot(aes(x = groupMembers, y = rsvps), data = membersWithGroupCounts) + 
  geom_point()

with(membersWithGroupCounts, cor(rsvps, groupMembers))
```

```{r}
plotPredictedActual = function(data, x = "predictedRSVPs", y = "rsvps") {
  ggplot(aes_string(x = x, y = y), data = data) + 
  geom_point() + 
  geom_abline(intercept=0, slope=1)
}

rmse = function(y, h) {
  return(sqrt(mean((y - h) ^ 2)))
}
```

### level/level

```{r}
fit = lm(rsvps ~ groupMembers, data = membersWithGroupCounts)
summary(fit)

membersWithGroupCounts$predictedRSVPs = predict(fit, membersWithGroupCounts)
with(membersWithGroupCounts, cor(rsvps, predictedRSVPs))

plotPredictedActual(membersWithGroupCounts, "predictedRSVPs", "rsvps")

ggplot(aes(x = groupMembers, y = rsvps), data = membersWithGroupCounts) +
  geom_point() +
  geom_abline(intercept = fit$coef[1], slope = fit$coef[2])

membersWithGroupCounts %>% select(rsvps, predictedRSVPs)
```

### add in hours of day

```{r}
membersWithGroupCounts$hoursIntoDay = as.numeric(membersWithGroupCounts$eventTime - trunc(membersWithGroupCounts$eventTime, "day"), units="hours")

with(membersWithGroupCounts, cor(hoursIntoDay, rsvps))

ggplot(aes(x = hoursIntoDay, y = rsvps), data = membersWithGroupCounts) + geom_point()

summary(lm(rsvps ~ hoursIntoDay * groupMembers, data = membersWithGroupCounts))
summary(lm(rsvps ~ hoursIntoDay + groupMembers, data = membersWithGroupCounts))

fit = lm(rsvps ~ hoursIntoDay + groupMembers, data = membersWithGroupCounts)
summary(fit)

membersWithGroupCounts$predictedRSVPs = predict(fit, membersWithGroupCounts)
with(membersWithGroupCounts, cor(rsvps, predictedRSVPs))

plotPredictedActual(membersWithGroupCounts, "predictedRSVPs", "rsvps")
fit$coef

membersWithGroupCounts$residuals = membersWithGroupCounts$predictedRSVPs - membersWithGroupCounts$rsvps
ggplot(aes(x = predictedRSVPs, y = residuals), data = membersWithGroupCounts) + geom_point()
```


### log rsvps

```{r}
with(membersWithGroupCounts, cor(hoursIntoDay, log(rsvps)))
ggplot(aes(x = hoursIntoDay, y = log(rsvps)), data = membersWithGroupCounts) + geom_point()

summary(lm(log(rsvps) ~ hoursIntoDay * groupMembers, data = membersWithGroupCounts))
summary(lm(log(rsvps) ~ hoursIntoDay + groupMembers, data = membersWithGroupCounts))

fit = lm(log(rsvps) ~ hoursIntoDay + groupMembers, data = membersWithGroupCounts)
summary(fit)

membersWithGroupCounts$logRSVPs = log(membersWithGroupCounts$rsvps)
membersWithGroupCounts$predictedLogRSVPs = predict(fit, membersWithGroupCounts)
with(membersWithGroupCounts, cor(logRSVPs, predictedLogRSVPs))

plotPredictedActual(membersWithGroupCounts, "predictedLogRSVPs", "logRSVPs")
fit$coef

membersWithGroupCounts$residuals = membersWithGroupCounts$predictedLogRSVPs - membersWithGroupCounts$logRSVPs
ggplot(aes(x = predictedLogRSVPs, y = residuals), data = membersWithGroupCounts) + geom_point()

df = merge(c(1700), c(22.0, 21.0, 19.0, 18.5, 17.0), all = TRUE)
names(df) = c("groupMembers", "hoursIntoDay")
df$predictedRSVPs = predict(fit, df) %>% exp()
df
```

### with venue

```{r}
centre = c(-0.129581, 51.516578)
membersWithGroupCounts = membersWithGroupCounts %>% mutate(distanceFromCentre = distHaversine(cbind(lon, lat), centre))

membersWithGroupCounts = membersWithGroupCounts %>% filter(distanceFromCentre < quantile(membersWithGroupCounts$distanceFromCentre, 0.98))

with(membersWithGroupCounts, cor(distanceFromCentre, log(rsvps)))
with(membersWithGroupCounts, cor(distanceFromCentre, rsvps))
ggplot(aes(x = distanceFromCentre, y = log(rsvps)), data = membersWithGroupCounts) + geom_point()


summary(lm(log(rsvps) ~ hoursIntoDay + groupMembers + distanceFromCentre, data = membersWithGroupCounts))
summary(lm(log(rsvps) ~ hoursIntoDay + groupMembers, data = membersWithGroupCounts))

```

### level/log

```{r}
fit = lm(log(rsvps) ~ groupMembers, data = membersWithGroupCounts)
summary(fit)

membersWithGroupCounts$predictedRSVPs = exp(predict(fit, membersWithGroupCounts))
with(membersWithGroupCounts, cor(rsvps, predictedRSVPs))

plotPredictedActual(membersWithGroupCounts, "predictedRSVPs", "rsvps")

membersWithGroupCounts$residuals = membersWithGroupCounts$predictedRSVPs - membersWithGroupCounts$rsvps

ggplot(aes(x = predictedRSVPs, y = residuals), data = membersWithGroupCounts) + geom_point()
```

### log/log

```{r}
fitExp = lm(log(rsvps) ~ log(groupMembers), data = membersWithGroupCounts)
membersWithGroupCounts$logRsvps = log(membersWithGroupCounts$rsvps)
membersWithGroupCounts$logGroupMembers = log(membersWithGroupCounts$groupMembers)
summary(fit)

membersWithGroupCounts$predictedLogRSVPs = predict(fit, membersWithGroupCounts)
with(membersWithGroupCounts, cor(log(rsvps), predictedLogRSVPs))
plotPredictedActual(membersWithGroupCounts, "predictedLogRSVPs", "logRsvps")

ggplot(aes(x = logGroupMembers, y = logRsvps), data = membersWithGroupCounts) +
  geom_point() +
  geom_abline(intercept = fit$coef[1], slope = fit$coef[2])

# exp(predict(fitExp, data.frame(groupMembers = c(1000))))
```

```{r}
membersWithGroupCounts$logRsvps = log(membersWithGroupCounts$rsvps)
membersWithGroupCounts$logGroupMembers = log(membersWithGroupCounts$groupMembers)

membersWithGroupCounts = membersWithGroupCounts %>% filter(logRsvps > 0)

fitExp = lm(logRsvps ~ logGroupMembers, data = membersWithGroupCounts)
summary(fitExp)

membersWithGroupCounts$predictedLogRSVPs = predict(fitExp, membersWithGroupCounts)
with(membersWithGroupCounts, cor(logRsvps, predictedLogRSVPs))
plotPredictedActual(membersWithGroupCounts, "predictedLogRSVPs", "logRsvps")

ggplot(aes(x = logGroupMembers, y = logRsvps), data = membersWithGroupCounts) +
  geom_point() +
  geom_abline(intercept = fitExp$coef[1], slope = fit$coef[2])

exp(predict(fitExp, data.frame(logGroupMembers = log(c(1000, 3000)))))
```

```{r}
fit = lm(rsvps ~ groupMembers + month, data = membersWithGroupCounts)
membersWithGroupCounts$predictedRSVPs = predict(fit, membersWithGroupCounts)
plotPredictedActual(membersWithGroupCounts)
```

```{r}
fit = lm(rsvps ~ groupMembers + day + month, data = membersWithGroupCounts)
summary(fit)
membersWithGroupCounts$predictedRSVPs = predict(fit, membersWithGroupCounts)
plotPredictedActual(membersWithGroupCounts)
```

```{r}
fit = lm(rsvps ~ groupMembers + time, data = membersWithGroupCounts)
summary(fit)
membersWithGroupCounts$predictedRSVPs = predict(fit, membersWithGroupCounts)
plotPredictedActual(membersWithGroupCounts)

cor(membersWithGroupCounts$rsvps, membersWithGroupCounts$predictedRSVPs)

plot(fit)
```

### Correlation between time and number of RSVPs

```{r}
library(polycor)
membersWithGroupCounts$time = as.factor(membersWithGroupCounts$time)
hetcor(membersWithGroupCounts %>% select(time, rsvps))
hetcor(membersWithGroupCounts %>% select(groupMembers, rsvps))

with(membersWithGroupCounts, cor(time, rsvps))
```

### Linear Regression Model vs Regression Tree

```{r}
write.csv(membersWithGroupCounts, "/tmp/membersWithGroupCounts.csv")
membersWithGroupCounts = read.csv("/tmp/membersWithGroupCounts.csv")

library(gridExtra)


model1 = lm(rsvps ~ groupMembers + time + month + day, data = membersWithGroupCounts)
membersWithGroupCounts$pred1 = predict(model1, membersWithGroupCounts)
model1Plot = plotPredictedActual(membersWithGroupCounts, "pred1")
cor(membersWithGroupCounts$rsvps, membersWithGroupCounts$pred1)

model2 = ctree(rsvps ~ groupMembers + factor(time) + factor(month) + factor(day),  
               data = membersWithGroupCounts)
membersWithGroupCounts$pred2 = predict(model2, membersWithGroupCounts)
cor(membersWithGroupCounts$rsvps, membersWithGroupCounts$pred2)
model2Plot = plotPredictedActual(membersWithGroupCounts, "pred2")

grid.arrange(model1Plot,model2Plot, ncol = 1)

membersWithGroupCounts %>% select(g.name, day, month, time, groupMembers, rsvps, pred2) %>% filter(pred2 > 79 & pred2 < 85) %>% sample_n(20)
```

### Plotting residuals

```{r}
membersWithGroupCounts$residuals = membersWithGroupCounts$rsvps - membersWithGroupCounts$pred2
ggplot(aes(x = rsvps, y = residuals), data = membersWithGroupCounts) + geom_point()
ggplot(aes(x = pred2, y = residuals), data = membersWithGroupCounts) + geom_point()

membersWithGroupCounts$standardized = membersWithGroupCounts$residuals / sd(membersWithGroupCounts$residuals)
ggplot(aes(x = rsvps , y = standardized), data = membersWithGroupCounts) + geom_point()
ggplot(aes(x = pred2 , y = standardized), data = membersWithGroupCounts) + geom_point()
```

#### Are the random errors normally distributed?

```{r}
normal= ggplot(aes(x = residuals), data = membersWithGroupCounts) + geom_histogram(binwidth=5)

#qqnorm(membersWithGroupCounts$residuals)
#qqline(membersWithGroupCounts$residuals)

qqplot.data <- function (vec) # argument: vector of numbers
{
  # following four lines from base R's qqline()
  y <- quantile(vec[!is.na(vec)], c(0.25, 0.75))
  x <- qnorm(c(0.25, 0.75))
  slope <- diff(y)/diff(x)
  int <- y[1L] - slope * x[1L]

  d <- data.frame(resids = vec)

  ggplot(d, aes(sample = resids)) + stat_qq() + geom_abline(slope = slope, intercept = int)

}

normal = qqplot.data(membersWithGroupCounts$residuals)
variation = ggplot(aes(x = pred2 , y = standardized), data = membersWithGroupCounts) + geom_point()

time = ggplot(aes(x = time, y = rsvps), data = membersWithGroupCounts) + geom_point()
month = ggplot(aes(x = month, y = rsvps), data = membersWithGroupCounts) + geom_point()
day = ggplot(aes(x = day, y = rsvps), data = membersWithGroupCounts) + geom_point()

grid.arrange(normal, variation, time, month, day, ncol = 2)
```

### Looking at plots of variables against RSVPs

```{r}
library(car)
crPlot(model1, "time")
crPlots(model1)
plot(model1)

lm.influence(model1)$hat
```

### New model where we use just the hour of the day

```{r}
events = events %>% mutate(hour = as.numeric(format(eventTime, "%H")))
events %>% head()

deriveMembersWithGroupCounts = function(events) {
  events %>%
  mutate(
    groupMembers = by(events, 1:nrow(events), function(row) { 
        findMemberCount(row$g.name, as.character(row$eventTime))
      }) %>% 
      cbind() %>% 
      as.vector()    
    )
}

deriveMembersWithGroupCounts2 = function(events) {
  events %>%
    mutate(ind = row_number()) %>%
    group_by(ind) %>%
    mutate(groupMembers = findMemberCount(g.name, as.character(eventTime)))
}

membersWithGroupCounts = deriveMembersWithGroupCounts(events)

system.time(findMemberCount("Big Data London", "2013-02-20 18:30:00"))

system.time(deriveMembersWithGroupCounts(events))
system.time(deriveMembersWithGroupCounts2(events))

model3 = lm(rsvps ~ groupMembers + hour + month + day, data = membersWithGroupCounts)
membersWithGroupCounts$pred3 = predict(model3, membersWithGroupCounts)
cor(membersWithGroupCounts$rsvps, membersWithGroupCounts$pred3)
model3Plot = plotPredictedActual(membersWithGroupCounts, "pred3")

membersWithGroupCounts$residuals = membersWithGroupCounts$rsvps - membersWithGroupCounts$pred3
ggplot(aes(x = pred3, y = residuals), data = membersWithGroupCounts) + geom_point()

summary(model3)
plot(model3)

model4 = ctree(rsvps ~ groupMembers + hour + factor(month) + factor(day),  
               data = membersWithGroupCounts)

membersWithGroupCounts$pred4 = predict(model4, membersWithGroupCounts)
cor(membersWithGroupCounts$rsvps, membersWithGroupCounts$pred4)
model4Plot = plotPredictedActual(membersWithGroupCounts, "pred4")

membersWithGroupCounts$residuals = membersWithGroupCounts$rsvps - membersWithGroupCounts$pred4
ggplot(aes(x = pred4, y = residuals), data = membersWithGroupCounts) + geom_point()

plot(model4)


summary(model1)
summary(model3)
```


### Number of other events happening on that day

```{r}
numberOfEventsModel = lm(rsvps ~ numberOfOtherEvents, data = events)
events$pred5 = predict(numberOfEventsModel, events)

cor(events$rsvps, events$pred5)
ggplot(aes(x = pred5, y = rsvps), data = events) + geom_point()

summary(numberOfEventsModel)
```

### Day of month

```{r}
dayOfMonthModel = lm(rsvps ~ dayOfMonth, data = events)
events$pred6 = predict(dayOfMonthModel, events)

cor(events$rsvps, events$pred6)
ggplot(aes(x = pred6, y = rsvps), data = events) + geom_point()

summary(dayOfMonthModel)

dayOfMonthModel2 = ctree(rsvps ~ dayOfMonth), data = events)
events$pred7 = predict(dayOfMonthModel2, events)
cor(events$rsvps, events$pred7)
```

### Number of days/hours (i.e. meetup lag) since last meetup?
### Meetups in the two weeks around this event for that group
### Other meetups that week
### How many people came to the previous meetup?


```{r}
write.csv(membersWithGroupCounts %>% select(-c(logRSVPS, logRSVPs, logRsvps, predictedRSVPs, predictedLogRSVPs, residuals, logGroupMembers)) , "/tmp/membersWithGroupCounts.csv", row.names = FALSE)

df = read.csv("/tmp/membersWithGroupCounts.csv")
df$eventTime = as.POSIXct(df$eventTime)
df %>% sample_n(10) %>% select(event.name, g.name, eventTime, groupMembers, rsvps)

ggplot(aes(x = groupMembers, y = rsvps), data = df) + 
  geom_point()

fit = lm(rsvps ~ groupMembers, data = df)
fit$coef

df$predictedRSVPs = predict(fit, df)
with(df, cor(rsvps, predictedRSVPs))

df$hoursIntoDay = as.numeric(df$eventTime - trunc(df$eventTime, "day"), units="hours")
ggplot(aes(x = hoursIntoDay, y = rsvps), data = df) + 
  geom_point()

fit = lm(rsvps ~ hoursIntoDay, data = df)
fit$coef

df$predictedRSVPs = predict(fit, df)
with(df, cor(rsvps, predictedRSVPs))

fit = lm(rsvps ~ hoursIntoDay + groupMembers, data = df)
summary(fit)
fit$coef

df$predictedRSVPs = predict(fit, df)
with(df, cor(rsvps, predictedRSVPs))

fit = lm(rsvps ~ hoursIntoDay * groupMembers, data = df)
summary(fit)
fit$coef

df$predictedRSVPs = predict(fit, df)
with(df, cor(rsvps, predictedRSVPs))

ggplot(aes(x = distanceFromCentre, y = rsvps), data = df) + 
  geom_point()

fit = lm(rsvps ~ distanceFromCentre), data = df)
fit$coef

df$predictedRSVPs = predict(fit, df)
with(df, cor(rsvps, predictedRSVPs))

```


```{r}
df$residuals = fit$residuals
ggplot(aes(x = predictedRSVPs, y = residuals), data = df) + geom_point()

ggplot(df, aes(x = residuals)) + geom_density()
```

### Lag

```{r}
df = df %>% arrange(g.name, eventTime)
dfWithTimeSinceLastEvent = df %>% 
  group_by(g.name) %>% 
  mutate(previousEventTime = lag(eventTime), previousRSVPs = lag(rsvps)) %>% 
  mutate(timeSinceLastEvent = as.numeric(eventTime - previousEventTime, unit="days")) %>%
  filter(!is.na(timeSinceLastEvent))

ggplot(aes(y = rsvps, x = timeSinceLastEvent), data = dfWithTimeSinceLastEvent) + 
  geom_point() +
  scale_x_log10() +
  scale_y_log10()

ggplot(aes(y = log(rsvps), x = log(timeSinceLastEvent)), data = dfWithTimeSinceLastEvent) + 
  geom_point()

with(dfWithTimeSinceLastEvent, cor(log(rsvps), log(timeSinceLastEvent)))

lm(log(rsvps) ~ log(groupMembers) + log(timeSinceLastEvent) + log(hoursIntoDay), data = dfWithTimeSinceLastEvent) %>% 
  summary()

fit = lm(log(rsvps) ~ groupMembers + timeSinceLastEvent + hoursIntoDay, data = dfWithTimeSinceLastEvent)
fit$coef

dfWithTimeSinceLastEvent$predictedRSVPs = exp(predict(fit, dfWithTimeSinceLastEvent))
dfWithTimeSinceLastEvent$residuals = fit$residuals

with(dfWithTimeSinceLastEvent, cor(rsvps, predictedRSVPs))

ggplot(aes(x = predictedRSVPs, y = residuals), data = dfWithTimeSinceLastEvent) + geom_point()

with(dfWithTimeSinceLastEvent, cor(rsvps, previousRSVPs))

fit = lm(rsvps ~ previousRSVPs, data = dfWithTimeSinceLastEvent)
summary(fit)

dfWithTimeSinceLastEvent$predictedRSVPs = predict(fit, dfWithTimeSinceLastEvent)
dfWithTimeSinceLastEvent$residuals = fit$residuals
with(dfWithTimeSinceLastEvent, cor(rsvps, previousRSVPs))

ggplot(aes(x = predictedRSVPs, y = residuals), data = dfWithTimeSinceLastEvent) + geom_point()

lm(rsvps ~ previousRSVPs + groupMembers + hoursIntoDay, data = dfWithTimeSinceLastEvent) %>% summary()
lm(rsvps ~ previousRSVPs + groupMembers + hoursIntoDay, data = dfWithTimeSinceLastEvent) %>% summary()
fit = lm(rsvps ~ previousRSVPs + groupMembers + hoursIntoDay, data = dfWithTimeSinceLastEvent)

fit$coef

newdata = data.frame(previousRSVPs = c(58, 220), groupMembers = c(1747, 3500), hoursIntoDay = c(18.5, 19))
predict(fit, newdata, interval="confidence")


```