# Vectorise all the things

## Distance from the weekend

```{r message=FALSE}
library(dplyr)
library(lubridate)
library(geosphere)
options("scipen"=100, "digits"=4)
```

```{r}
times = ymd_hms("2002-01-01 17:00:00") + c(0:99) * hours(1)
data = data.frame(time = times)
data %>% head()
```

We want to find out how many hours away from the weekend they are.

### Non vectorised version


```{r}
distanceFromWeekend = function(dateToLookup) {
  before = floor_date(dateToLookup, "week") + hours(23) + minutes(59) + seconds(59)
  after  = ceiling_date(dateToLookup, "week") - days(1)
  timeToBefore = dateToLookup - before
  timeToAfter = after - dateToLookup
  
  if(timeToBefore < 0 || timeToAfter < 0) {
    0  
  } else {
    if(timeToBefore < timeToAfter) {
      timeToBefore / dhours(1)
    } else {
      timeToAfter / dhours(1)
    }
  }
}

system.time(
  data %>% mutate(ind = row_number()) %>% group_by(ind) %>% mutate(dist = distanceFromWeekend(time))  
  )

```

### Vectorised version
 
```{r}
distanceFromWeekendVectorised = function(dateToLookup) {
  before = floor_date(dateToLookup, "week") + hours(23) + minutes(59) + seconds(59)
  after  = ceiling_date(dateToLookup, "week") - days(1)
  pmin(pmax(dateToLookup - before, 0), pmax(after - dateToLookup, 0)) / dhours(1)
}

system.time(data %>% mutate(dist = distanceFromWeekendVectorised(time)))
```

## Extracting start date

```{r}
googleTrends = read.csv("/Users/markneedham/Downloads/report.csv", row.names=NULL)
names(googleTrends) = c("week", "score")
googleTrends %>% head(10)
```

### Non vectorised version

```{r}
system.time(
  googleTrends %>% 
    mutate(ind = row_number()) %>% 
    group_by(ind) %>%
    mutate(dates = strsplit(week, " - "),
           start = dates[[1]][1] %>% strptime("%Y-%m-%d") %>% as.character())
  )
```

This one isn't very easy to vectorise unless we change the function we're using - # http://stackoverflow.com/questions/3054612/r-strsplit-and-vectorization

### Vectorised version

```{r}
system.time(googleTrends %>% mutate(start = substr(week, 1, 10) %>% ymd()))
```

## Calculating haversine distance

```{r}
venues = read.csv("/tmp/venues.csv")
venues %>% head()
centre = c(-0.129581, 51.516578)
```

### Non vectorised version

```{r}
system.time(venues %>% 
  mutate(distanceFromCentre = by(venues, 1:nrow(venues), function(row) { distHaversine(c(row$lon, row$lat), centre)  }))
  )
```

### Vectorised version

```{r}
system.time(venues %>% mutate(distanceFromCentre = distHaversine(cbind(venues$lon, venues$lat), centre)))
```

## Finding how many members there were on a specific date

https://gist.github.com/mneedham/6ec5651f0402fd4ca22e

```{r}
cumulativeMeetupMembers = read.csv("/tmp/cumulativeMeetupMembers.csv")
cumulativeMeetupMembers %>% sample_n(10)

cumulativeMeetupMembers %>% head(10)

dates = ymd("2014-09-01") + c(0:9) * weeks(1)
groups = cumulativeMeetupMembers %>% distinct(g.name) %>% select(g.name)

groupsOnDate = merge(dates, groups)
names(groupsOnDate) = c('date', 'name')
groupsOnDate %>% sample_n(10)
```

### Non vectorised version 

```{r}
memberCount = function(meetupMembers) {
  function(groupName, date) {
    (meetupMembers %>% 
       filter(g.name == groupName & dayMonthYear < date) %>% do(tail(., 1)))$n    
  }  
} 

findMemberCount = memberCount(cumulativeMeetupMembers)

system.time(groupsOnDate %>% mutate(groupMembers = by(groupsOnDate, 1:nrow(groupsOnDate), function(row) { 
        findMemberCount(row$name, as.character(row$date))
      }) %>% 
      cbind() %>% 
      as.vector() ))
```

### Vectorised version

```{r}
memberCount = function(meetupMembers) {
  function(groupName, date) {
    print(groupName)
    print(date)
    x = (meetupMembers %>% 
       mutate(key = paste(groupName, "foo")) %>%
       filter(g.name %in% groupName )%>%
       group_by(key) %>%
       do(tail(., 1)))
    print(x)
    x$n
  }  
} 

findMemberCount = memberCount(cumulativeMeetupMembers)

groupsOnDate %>% mutate(date = date) %>% (groupMembers = findMemberCount(name, date))

cumulativeMeetupMembers %>% head()

cumulativeMeetupMembers %>% 
  filter(g.name %in% c('Neo4j - London User Group', 'Big Data / Data Science / Data Analytics Jobs') &
           dayMonthYear < c(ymd("2014-11-06", "2013-02-07")))

groupNames = c('Neo4j - London User Group', 'Big Data / Data Science / Data Analytics Jobs')
dates = c(ymd("2011-12-12"), "2013-12-12"))
events = c(1,2)

blah = merge(cumulativeMeetupMembers, events)

cumulativeMeetupMembers %>% 
  mutate(dayMonthYear = ymd(dayMonthYear)) %>% 
  mutate(diff = difftime(dates, dayMonthYear)) %>%
  filter(diff > 0 )

blah %>% 
  mutate(dayMonthYear = ymd(dayMonthYear)) %>% 
  filter(g.name %in% groupNames & difftime(dates, dayMonthYear) > 0 ) %>%
  group_by(y) %>%
  do(tail(., 1))

cumulativeMeetupMembers %>% 
  mutate(dayMonthYear = ymd(dayMonthYear)) %>% 
  mutate(event = events)
  filter(g.name %in% groupNames & difftime(dates, dayMonthYear) > 0 ) %>%
  
  filter(min_rank(desc(n)) <= 2 & n > 0)



cumulativeMeetupMembers %>% 
  filter(g.name %in% groupNames & difftime(dates, dayMonthYear) < 0) %>%
  group_by(key) %>%
  do(tail(., 1)) %>%
  ungroup() %>%
  head()

cumulativeMeetupMembers %>% 
    mutate(key = paste(groupNames, dates)) %>% 
    filter(g.name %in% groupNames) %>%
    group_by(key) %>%
    do(tail(., 1)) %>%
    ungroup() %>%
    head()


groupsOnDate %>% head()
cumulativeMeetupMembers %>% head()
```

